Industrial Applications of CFD

### 2011-03-15 MSTE_methodology.tex
casi listo, falta unos TODO relacionados con LSQ y limpiar la biblio... y algo mas?

\section{Introduction}
\Fede{FEDE WAS HERE!!! Faltan algunas referencias, y tenemos que coordinarlas. Ponele, mi primer paper en CFD lo cito como Sporleder2010, pero creo que vos lo ten\'es como "sporleder" Intent\'e abrir el .bib con mi JabRef, pero me tir\'o error. Propongo indicar cambios que cada uno haga en las secciones en com\'un o secciones ajenas (si yo agrego una ecuaci\'on al explicar LSQ no indico nada, pero si lo hago en la intro s\'i, x ej.). Ah, y me sigue tirando errores de paquetes. A vos no? Tengo 13 errores y 33 bad boxes ahora :-D }

@@

\TODO{No he leido esta seccion todavia}
Using variational analysis, minimizing the functional $\mathcal{J}(\mathbf{f})$ is equivalent to finding $\mathbf{f} \in X(\Omega)$ such that:

@@

In the manufacturing solution method we propose a solution $\phi(\xi, z)$ and calculate analitically the value of the source. For this problem the values chosen are:

@@

\noindent Choosing the values A=, V=, M= and M= \TODO{no me acuerdo}.

\TODO{Mention implementation details (polynomials and quadratures used, number of points, solver, etc.).  ouch... GLL, 12 puntos como se ve en la figura}

@@

Both the discharge, $q({\xi})$ and the porosity, $\epsilon({\xi})$ do not depend on the position along the column. Plot of the distribution and cummulative distribution for these two functions are given in Figure \ref{fig:profiles}.

@@

The solution is shown in Figure \ref{fig:solution}. As the liquid flows down the column $\phi$ increases due to reactions happening inside the pores. Despite the source term is very different for different pore sizes (negative for large pores and positive for small pores, see Figure \ref{fig:source}) the tracer $\phi$ is exchanged between different pores scales tending to level out the differences. However the increase is larger for the small pores at all the length of the column (z values). The source term (Figure \ref{fig:source}) behaves differently for different pore scales. Large amounts of $\phi$ are generated for pores smaller than 5 mm, while a sink is observed in the largest pores. This behaviour for the source term mimic two compiting reactions. It models the case of a specie that is a product of an heterogeneous reaction but is a reactant of a reaction taking place in the liquid bulk. Heterogeneous reactions depend strongly of the surface to volume ratio which is much larger for small pore scales. At the same time the reactant is consumed in the larger pores in this case as the bulk reaction that consumes $\phi$ becomes more dominant.

@@

\TODO{Show and comment on convergence plot}

@@

\begin{itemize}
\item The least square high order method is well suited for the solution of the multi-scale transport equation for porous media achieving exponencial convergence in the method order.
\item A method has been described and can now be applied for the solution of transport and reactions problems in porous media.
\end{itemize}

>>>>

\section{Introduction}
%\Fede{FEDE WAS HERE!!! Faltan algunas referencias, y tenemos que coordinarlas. Ponele, mi primer paper en CFD lo cito como Sporleder2010, pero creo que vos lo ten\'es como "sporleder" Intent\'e abrir el .bib con mi JabRef, pero me tir\'o error. Propongo indicar cambios que cada uno haga en las secciones en com\'un o secciones ajenas (si yo agrego una ecuaci\'on al explicar LSQ no indico nada, pero si lo hago en la intro s\'i, x ej.). Ah, y me sigue tirando errores de paquetes. A vos no? Tengo 13 errores y 33 bad boxes ahora :-D }

@@

\Pablo{No he leido esta seccion todavia en mucho detalle. Pero parece estar bien. Si es la primera vez que se publica este tipo de informacion decime que agarro la lupa y la miro en mas detalle... se la podes dar a Hugo a ver si la entiende, jeje }
Using variational analysis, minimizing the functional $\mathcal{J}(\mathbf{f})$ is equivalent to finding $\mathbf{f} \in X(\Omega)$ such that:

@@

In the manufacturing solution method we propose a solution $\phi(\xi, z)$ and calculate analitically the value of the source. For this problem the chosen values are:

@@

\TODO{Mention implementation details (polynomials and quadratures used, number of points, solver, etc.).  ouch... GLL, 12 puntos como se ve en la figura} \Pablo{Ya esta, podemos quitar este TODO?}

\noindent Choosing the values $A=\tfrac{1}{500}$, $V=0.001$, $M=1$ and pore scale limits $\xi_0=1$ and $\xi_f=10$ mm. Gauss-Legendre-Lobato points where chosen for the external coordinate and Gauss-Legendre for the internal coordinate. \Pablo{revisa que tenga sentido esta oracion por favor...}

@@

Both the discharge, $q({\xi})$ and the porosity, $\epsilon({\xi})$ do not depend on the position along the column. Plot of the distribution and cumulative distribution for these two functions are given in Figure \ref{fig:profiles}.

@@

The solution is shown in Figure \ref{fig:solution}. As the liquid flows down the column $\phi$ increases due to reactions happening inside the pores. Despite the source term is very different for different pore sizes (negative for large pores and positive for small pores, see Figure \ref{fig:source}) the tracer $\phi$ is exchanged between different pores scales tending to level out the differences. However the increase is larger for the small pores at all the length of the column (z values). The source term (Figure \ref{fig:source}) behaves differently for different pore scales. Large amounts of $\phi$ are generated for pores smaller than 5 mm, while a sink is observed in the largest pores. This behaviour for the source term mimic two competing reactions. It models the case of a specie that is a product of an heterogeneous reaction but is a reactant of a reaction taking place in the liquid bulk. Heterogeneous reactions depend strongly of the surface to volume ratio which is much larger for small pore scales. At the same time the reactant is consumed in the larger pores in this case as the bulk reaction that consumes $\phi$ becomes more dominant.

@@

%\TODO{Show and comment on convergence plot}
Finally, the polynomial order for both dimensions was varied from 5 to 12 to verify if the numerical solution approximates to the proposed analytical solution. The infinity norm error is shown in the Figure \ref{fig:convergence} where it can be seen that the error is reduced exponentially with the method order up to computer precision.

@@

\begin{itemize}
\item The least square high order method is well suited for the solution of the multi-scale transport equation for porous media achieving exponential convergence in the method order.
\item A method has been described and can now be applied for the solution of transport and reactions problems in porous media.
\end{itemize}
